### 2025-04-09 README.Rmd
RENDER
Include Singapore open data licence acknowledgement

# traveltime

@@

>>>>

# `traveltime`

@@

## Imported data
This repository contains information from the dataset "LTA MRT Station Exit (GEOJSON)" accessed on the 10th of December 2024 from  [data.gov.sg](https://data.gov.sg/datasets/d_b39d3a0871985372d7e1637193335da5/view), which is made available under the terms of the Singapore Open Data Licence version 1.0 <https://data.gov.sg/open-data-licence>
